---
title: "Marketing Spend Performance"
author: "YU-LIN CHUNG, 35480351"
format:
    html:
        toc: true
        theme: solar
    pdf:
        toc: true
---
```{r setup}
#| echo: FALSE
#| warning: false
#| message: false
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE)

library(tidyverse)
```

# Introduction


# Research Question
This report uses customer data on marketing spend and purchase amounts to investigate whether higher marketing spend per customer leads to higher purchase amounts, as well as whether this relationship differs across segments, including Consumer, SMB, and Enterprise groups.

# Dataset Introduction
```{r}
data <- read.csv(here::here("data/35480351_Yu-Lin Chung.csv"))
str(data)
clean_data <- data %>%
    drop_na(purchase_amount)%>%
  mutate(signup_date = as.Date(signup_date))
```

The database includes marketing information for `r nrow(data)` customers, each with a unique ID. Additionally, it includes their sign-up dates, customer types, marketing spend of campaign, number of visitors, purchase amounts, and some notes.

I observed that some purchase amount data was missing, which may cause issues. Therefore, I removed the rows that contain "NULL" values. Additionally, the format of customers' sign-up dates was inconsistent,, therefore I adjusted it to make the table clearer.

# Dataset Description
```{r}
#| fig-cap: "Number of customers in each customer segment."
mean_segment <- clean_data %>%
    group_by(segment) %>%
  summarise(
    mean_marketing_spend = mean(marketing_spend),
    mean_purchase_amount = mean(purchase_amount)
  )
mean_segment

count_segment <- clean_data %>%
    count(segment)
ggplot(count_segment, aes(x = segment, y = n))+
    geom_col()+
    geom_text(aes(label = n), vjust = -0.3) +
    labs(title =  "Number of Customers by Segment",
    x = "Customer Segment",
    y = "Number of Customers")
```

After cleaning data, the dataset contains `r nrow(clean_data)` observations and `r ncol(clean_data)` variables. The numerical variables are marketing spend, visits, and purchase amount, while the non-numerical variables include customer ID, sign-up date, segment and notes. Expecially, segment is a categorical variable which separates customers in different gropus, such as "SMB", "Consumer" and "Enterprise".

# Results
```{r}
#| label: fig-scatterplot
#| fig-cap: "Relationship between marketing spend and purchase amount."
ggplot(clean_data, aes(x = marketing_spend, y = purchase_amount))+
    geom_point()+
    labs(title = "Marketing Spend and Purchase Amount",
    x = "Marketing Spend",
    y = "Purchase Amount")
```

```{r}
#| label: fig-facetwrap
#| fig-cap: "Relationship between marketing spend and purchase amount across customer segments."
ggplot(clean_data, aes(x = marketing_spend, y = purchase_amount)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ segment) +
  labs(x = "Marketing Spend",
  y = "Purchase Amount")
```

@fig-scatterplot shows a positive relationship between marketing spend and purchase amounts, suggesting that higher marketing spend per customer leads to higher purchase amounts on this marketing campaign performance.

Furthermore,  @fig-facetwrap shows that this positive relationship exists across all type of customer, including Consumer, SMB and Enterprise. The positive relationship can be clearly seen in both Consumer and SMB, although SMB segment shows slightly more variability than the Consumer segment. In particular, the Enterprise segment has fewer observations, which suggests that conclusions about this segment should be made more cautiously.
